### 2016-05-26 main.tex
Correctly added some cites and bibliography
Added intro chapter (commented PDF images)
minor changes
few changes
added new paper
Added Acknowledgements

%The acknowledgements and the people to thank go here, don't forget to include your project advisor\ldots
%\input{acknowledgements}

@@

\textbf{DMP} & \textbf{D}iscrete \textbf{M}aximum \textbf{P}rinciple \\

\end{abbreviations}

@@

%\begin{symbols}%{lll} % Include a list of Symbols (a three column table)
%\input{symbols_definition}
%\end{symbols}

@@

@@

\input{Chapters/paper2}

@@

%\printbibliography[heading=bibintoc]
\bibliography{art004,ar009,hp-adaptivity}

>>>>

Desde 2015 hay un poquito de Guatemala en m\'i, de la cosmovisión ind\'gena de quienes nos acogieron en sus casas, dels Quetzals Rebeldes que em van acompanyar en aquesta aventura y, sobretodo, de la gente bonita de la Plataforma de Barcelona que ha sabido recogerme, levantarme y abrazarme, ponerle la piel necesaria, a este \'utimo año de doctorado.
%The acknowledgements and the people to thank go here, don't forget to include your project advisor\ldots
%\input{acknowledgements}

@@

\textbf{DMP} & \textbf{D}iscrete \textbf{M}aximum \textbf{P}rinciple \\
\textbf{GJV} & \textbf{G}radient \textbf{J}ump \textbf{V}iscosity
\end{abbreviations}

@@

\input{symbols_definition}

@@

\input{Chapters/intro}

@@

%\input{Chapters/paper2}

\input{Chapters/paper3}

@@

%\printbibliography[heading=bibintoc]
\bibliography{art004,art009,hp-adaptivity}
